\begin{thebibliography}{99}
	\bibitem{skincolor:obr} \textit{Dostupné z: \url{http://humanorigins.si.edu/sites/default/files/styles/home_slider_phablet/public/KidComp_landscape.jpg}}
	\bibitem{openCV:sklansky}SKLANSKY, Jack. \textit{Finding the convex hull of a~simple polygon.} [online] Pattern Recognition Letters, December 1982 . [cit. 11.03.2018].
		\textit{Dostupné z: \url{http://www.sciencedirect.com/science/article/pii/0167865582900162}}
	\bibitem{mog:zivkovic}ZIVKOVIC, Zoran. \textit{Improved adaptive Gausian mixture model for background subtraction.} [online] International Conference Pattern Recognition, UK, August, 2004 [cit. 11.03.2018].
		\textit{Dostupné z: \url{http://www.zoranz.net/Publications/zivkovic2004ICPR.pdf}}
	%\bibitem{edgeTemplate} PAPAGEORGIU Constantine, POGGIO Tomaso A. \textit{A Trainable Pedestrian Detection System} [online] International Journal of Computer Vision (IJCV), November, 2000  [cit. 20.03.2018]. 
 	%	\textit{Dostupné z: \url{https://www.researchgate.net/publication/2467374_A_Trainable_Pedestrian_Detection_System}}
 %	\bibitem{partModels} CHO, Hyunggi, RYBSKI, Paul, BAR-HILLER, Aharon, ZHANG, Wende,  \textit{Real-time pedestrian detection with deformable part models} [online] IEEE, July 05, 2012  [cit. 20.03.2018]. 
 %		\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/6232264/}}
% 	\bibitem{edgelet} WU, Bo, NEVATIA Ram, \textit{Detection of multiple, partially occluded humans in a single image by Bayesian combination of edgelet part detectors} [online] IEEE, December, 2005 [cit. 20.03.2018]. 
 %		\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/1541243/}}
 %	\bibitem{orientationFeatures} MIKOLAJCZYK, Krystian, SCHMID, Cordelia, ZISSERMAN, Andrew, \textit{Human detection based on a probabilistic assembly of robust part detectors} [online] ECCV, 2004 [cit. 20.03.2018]. 
% 		\textit{Dostupné z: \url{https://link.springer.com/chapter/10.1007/978-3-540-24670-1_6}}
% 	\bibitem{leibe} LEIBE, Bastian, SEEMANN, Edgar, SCHIELE Bernt, \textit{Pedestrian detection in crowded scenes} [online] IEEE, July 25, 2005 [cit. 20.03.2018]. 
% 		\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/1467359/}}
% 	\bibitem{motionAlg1} BARNICH, Olivier, JODOGNE, Sébastien, DROOGENBROECK, Marc, Van, \textit{Robust analysis of silhouettes by morphological size distributions} [online] Advanced Concepts for Intelligent Vision Systems(ACIVS), 2006 [cit. 20.03.2018]. 
% 		\textit{Dostupné z: \url{https://link.springer.com/chapter/10.1007/11864349_67}}
% 	\bibitem{motionAlg2} PIÉRARD, Sébastien, LEJEUNE, Anne, DROOGENBROECK, Marc, Van, \textit{A probabilistic pixel-based approach to detect humans in video streams}  [online] IEEE, July 12, 2011  [cit. 20.03.2018]. 
% 		\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/5946555/}}
% 	\bibitem{multiCameras} FLEURET Francois, BERCLAZ, Jerome, LENGAGNE Richard, FUA, Pascal, \textit{Multi-Camera People Tracking with a Probabilistic Occupancy Map} [online] IEEE, December 18, 2007  [cit. 20.03.2018]. 
 		\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/4359319/}}
	\bibitem{openCV:MOG}ITSEEZ, Open Source Computer Vision documentation v3.2.0 \textit{How to Use Background Subtraction Methods} [online] Itseez, April, 2014 [cit. 11.03.2018].
		\textit{Dostupné z: \url{http://docs.opencv.org/3.2.0/d1/dc5/tutorial_background_subtraction.html}}
	\bibitem{hog:dalal} {DALAL, Navneet, TRIGGS, Bill. \textit{Histogram of oriented gradients for human detection}. [online] IEEE, July 25, 2005. [cit. 11.03.2018].
		\textit{Dostupné z: \url{https://lear.inrialpes.fr/people/triggs/pubs/Dalal-cvpr05.pdf}}}
	\bibitem{shapeContext} BELONGIE, Serge, MALIK, Jitendra, \textit{Matching with shape contexts}. [online] IEEE, August 06, 2002 [cit. 30.03.2018]. 
 		\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/853834/}}
 	\bibitem{siftPaper} LOWE, David, \textit{Object recognition from local scale-invariant features}. [online] IEEE, September, 1999 [cit. 30.03.2018]. 
 		\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/790410/}}
	\bibitem{hog:obr} \textit{Dostupné z: \url{http://www.learnopencv.com/wp-content/uploads/2016/11/hog-cells.png}}
	\bibitem{libsvm} CHANG, Chih-Chung, LIN, Chin-Jen, \textit{LIBSVM: A~Library for Support Vector Machines}. [online] ACM Transactions on Intelligent Systems and Technology, 2001 [cit. 31.03.2018]. 
 		\textit{Dostupné z: \url{https://www.csie.ntu.edu.tw/~cjlin/libsvm/}}
 	\bibitem{kernlab} KARATZOGLOU, Alexandros, SMOLA, Alex, HORNIK, Kurt, ZEILEIS, Achim \textit{kernlab -- An {S4} Package for Kernel Methods in {R}}. [online] Journal of Statistical Software, 2004 [cit. 31.03.2018]. 
 		\textit{Dostupné z: \url{}}
 	\bibitem{scikit-learn} PEDREGOSA, F., VAROQUAUX, G., GRAMFORT, A., MICHEL, V., THIRION, B., GRISEL, O., BLONDEL, M., PRETTENHOFER, P., WEISS, R., DUBOURG, V., VANDERPLAS, J., PASSOS, A., COURNAPEAU, D., BRUCHER, M., PERROT, M., DUCHESNAY, E., \textit{Scikit-learn: Machine Learning in Python}. [online] Journal of Machine Learning Research, 2011 [cit. 31.03.2018]. 
			\textit{Dostupné z: \url{http://support.sas.com/documentation/cdl/en/whatsnew/64209/HTML/default/viewer.htm\#emdocwhatsnew71.htm}}
 	\bibitem{svmlight} JOACHIMS, Thorsten \textit{Making large-Scale SVM Learning Practical. Advances in Kernel Methods - Support Vector Learning}. [online] MIT-Press, 1999 [cit. 31.03.2018]. 
 		\textit{Dostupné z: \url{http://svmlight.joachims.org/}}
	\bibitem{svm:vapnik} VAPNIK, Vladimir, CORTES, Corinna, \textit{Support-vector networks}. [online] Kluwer Academic Publishers, February 20, 1995 [cit. 30.03.2018]. 
 		\textit{Dostupné z: \url{https://link.springer.com/article/10.1007\%2FBF00994018}}
	\bibitem{svmsucc} KOWALCZYK, Alexandre.  \textit{Support Vector Machines Succinctly}.  [online] Syncfusion, Published on October 23, 2017 [cit. 11.03.2018]. 
		\textit{Dostupné z: \url{https://www.syncfusion.com/ebooks/support_vector_machines_succinctly}}
	\bibitem{csvmclass} BOSER, Bernhard, GUYON, Isabelle, VAPNIK, Vladimir, \textit{A~training algorithm for optimal margin classifiers}. [online] ACM Press, 1992 [cit. 01.04.2018]. 
 		\textit{Dostupné z: \url{http://citeseerx.ist.psu.edu/viewdoc/summary?doi=10.1.1.21.3818}}
 	\bibitem{nusvmsvrclass} SCHÖLKOPF, Bernhard, SMOLA, Alex, WILLIAMSON, Robert, BARTLETT, Peter, \textit{New support vector algorithms}. [online] MITP, Neural Computation, May 1, 2000 [cit. 01.04.2018]. 
 		\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/6790203/}}
 	\bibitem{oneclasssvm} SCHÖLKOPF, Bernhard, PLATT, John, SHAWE-TAYLOR, John, SMOLA, Alex, WILLIAMSON, Robert, \textit{Estimating the support of a~high-dimensional distribution}. [online] MITP, Neural Computation, July 1, 2001 [cit. 01.04.2018]. 
 		\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/6790022/}}
 	\bibitem{svrsvm} VAPNIK, Vladimir \textit{Fast training of support vector machines using sequential minimal optimization.}. Wiley, New York, NY, 1998. 
 	\bibitem{haar:like} HOANG, Van-Dung, VAVILIN, Andrey, JO, Kang-Hyun, \textit{Pedestrian detection approach based on modified Haar-like features and AdaBoost}. [online] IEEE, October, 2012 [cit. 31.03.2018]. 
 		\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/6393256/}}
 	%\bibitem{haar:like2} LIENHART, R, Maydt, J,  \textit{An extended set of Haar-like features for rapid object detection}. IEEE, December, 2002 [cit. 31.03.2018]
 	%	\textit{Dostupné z: \url{https://ieeexplore.ieee.org/document/1038171/}}
 	\bibitem{violajones} VIOLA, Paul, JONES, Michael, \textit{Robust real-time face detection}. [online] IEEE, August 07, 2002 [cit. 31.03.2018]. 
 		\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/937709/}}
 	\bibitem{lbp:texture} HE, Dong-chen, WANG, Li, \textit{Texture Unit, Texture Spectrum, And Texture Analysis}. [online] IEEE, July, 1990 [cit. 02.04.2018]. 
 		\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/572934/}}
 	\bibitem{lbp:first} OJALA, T, PIETIKAINEN, M, HARWOOD, D, \textit{Performance evaluation of texture measures with classification based on Kullback discrimination of distributions}. [online] ICPR, Proceedings of the 12th IAPR International Conference on Pattern Recognition, 1994 [cit. 02.04.2018]. 
 		\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/576366/}}
	\bibitem{lbp:orig} AHONEN, Timo, HADID, Abdenour, PIETIKAINEN, Matti, \textit{Face Description with Local Binary Patterns: Application to Face Recognition}. [online] IEEE, October 30, 2006 [cit. 31.03.2018]. 
 		\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/1717463/}}
 	\bibitem{adaboost} FREUND, Yoav, E. SCHAPIRE, Robert, \textit{A~Decision-Theoretic Generalization of On-Line Learning and an Application to Boosting}. [online] Journal of Computer and System Sciences vol. 55, 1997 [cit. 01.04.2018]. 
 		\textit{Dostupné z: \url{https://www.sciencedirect.com/science/article/pii/S002200009791504X}}
 	\bibitem{hoglpb} WANG, Xiaoyu, HAN, Tony X, YAN, Shuicheng, \textit{An HOG-LBP human detector with partial occlusion handling}. [online] IEEE, July 29, 2010 [cit. 31.03.2018]. 
 	\textit{Dostupné z: \url{http://ieeexplore.ieee.org/document/5459207/}}
	\bibitem{fig:mlvsann} \textit{Dostupné z: \url{https://cdn-images-1.medium.com/max/800/1*ZX05x1xYgaVoa4Vn2kKS9g.png}}
	\bibitem{ann} HILTZ, Frederick, \textit{Analog Computer Simulation of a~Neural Element}. [online] IEEE, January, 1962 [cit. 16.04.2018]. 
 	\textit{Dostupné z: \url{https://ieeexplore.ieee.org/document/4322944/}}
 	\bibitem{lenet} LE CUN, Yann, JACKEL Lawrence, BOSER Bernhard, DENKER John, GRAF, Hans, GUYON, Isabelle, HENDERSON, William, HOWARD, Richard, HUBBARD, Douglas, \textit{Handwritten digit recognition: applications of neural network chips and automatic learning}. [online] IEEE, November, 1989 [cit. 16.04.2018]. 
 	\textit{Dostupné z: \url{https://ieeexplore.ieee.org/document/41400/}}
 	\bibitem{sudipdas} Dostupné z: \url{https://www.kaggle.com/sudipdas/datasets}
 	\bibitem{inria} Dostupné z: \url{http://pascal.inrialpes.fr/data/human/}
 	\bibitem{eth} Dostupné z: \url{https://data.vision.ee.ethz.ch/cvl/aess/}
 	\bibitem{tudbrussels} Dostupné z:  

		\url{https://www.mpi-inf.mpg.de/departments/computer-vision-and-multimodal-computing/research/people-detection-pose-estimation-and-tracking/multi-cue-onboard-pedestrian-detection/}
 	\bibitem{kitti} Dostupné z: \url{http://www.cvlibs.net/datasets/kitti/eval_object.php}
 	\bibitem{daimler} Dostupné z: \url{http://www.gavrila.net/Datasets/Daimler_Pedestrian_Benchmark_D/Daimler_Mono_Ped__Detection_Be/daimler_mono_ped__detection_be.html}
 	\bibitem{daimlerstereo} Dostupné z: \url{http://www.gavrila.net/Datasets/Daimler_Pedestrian_Benchmark_D/Daimler_Stereo_Ped__Detection_/daimler_stereo_ped__detection_.html}
 	\bibitem{caltech} Dostupné z: \url{http://www.vision.caltech.edu/Image_Datasets/CaltechPedestrians/datasets/USA/}
 	\bibitem{peta} Dostupné z: \url{http://mmlab.ie.cuhk.edu.hk/projects/PETA.html}
 	\bibitem{cuhk} Dostupné z: \url{http://www.ee.cuhk.edu.hk/~xgwang/CUHK_identification.html}
\end{thebibliography}
